---
title: "Literate analysis"
format: html
---

## Introduction

### About this data

This dataset contains seawater chemstiry data from the Artic Ocean near the North Pole from 2000-2014. This data was accessed on June 26, 2023 from the [Artic Data Center](https://arcticdata.io/catalog/view/doi:10.18739/A25T3FZ8X).

### Setup
```{r}
# libraries
```

### Reading in data
```{r}
#| warning: false
#| message: false

bgChem <- read.csv("https://arcticdata.io/metacat/d1/mn/v2/object/urn%3Auuid%3A35ad7624-b159-4e29-a700-0c0770419941")
```

Exploring the data

```{r}
#| eval: false
#| echo: false

head(bgChem)
str(bgChem)
summary(bgChem)
```


## Analysis

### Calculate summary statistics
```{r}
nitrate <- mean(bgChem$NO3)
nitrite <- mean(bgChem$NO2)
amm <- mean(bgChem$NH4)
phos <- mean(bgChem$P)
```

### Calculate mean Redfield Ratio

```{r}
ratio <- (nitrate + nitrite + amm)/phos
```

### Plot Redfield Ratio

```{r}
plot(bgChem$P, bgChem$NO2 + bgChem$NO3 + bgChem$NH4)
```


## Conclusion

The Redfield Ratio for this dataset is approximately `r round(ratio)`.